%-------------------------------------------------------
%    DOCUMENT CONFIGURATIONS
%-------------------------------------------------------

%-------------------------------------------------------
%    START OF MANAGEMENT PAGE
%-------------------------------------------------------
\subsection{Management}
An iterative approach has been used during the progress of the project. So, the SCRUM methodology was chosen. The Backlog and the Sprint advances can be found in the annexes.

The project planning has been done for eight weeks. It was divided into eight sprints starting and ending at each week Wednesday. We will be using the software called Vivifyscrum to digitalize the scrum process; the school will be paying the 10\$ fee for each month of the project.

A global replanning was made during the second sprint because objectives weren't clearly defined and the tasks were too detailed (and maybe unrealistic on the long term).

At the end of Sprint 3, a replanning has been made due to multiple problems with the Ethereum network. It was decided to focus on the decentralized storage.

As the project ended, all the weekly objectives had been respected expect for the consensus related implementations.

Based on the student's log, the time requirement for the project of 340h has been made with 341.25h. The R\&D itself as produced 289.50h:

\begin{itemize}
\item Research: 149.00h
\item Development: 140.50h
\end{itemize}

We can note that starting during development, the student had usually forgotten to use the \textit{Vivifyscrum}, however, the student log was kept updated.

%-------------------------------------------------------
%    END OF MANAGEMENT PAGE
%-------------------------------------------------------
