%-------------------------------------------------------
%    DOCUMENT CONFIGURATIONS
%-------------------------------------------------------

%-------------------------------------------------------
%    START OF OBJECTIVES PAGE
%-------------------------------------------------------
\subsection{Objectives}

As it is today, the data is centralized into specific operators like Google, Facebook, Dropbox, Tor hidden services, and much more (expect of services like Freenet\cite{Clarke2001Freenet:System}). They are usually using encrypted protocol to transmit data to their client but are most of the time stored in clear on their cloud servers. Sometimes the data is stored encrypted, but the operators must comply with the local laws of the data centers, which could compromise the security. The user could encrypt the data himself; however, technical knowledge is required and sometimes the rules of the storage operators does not allow homemade security due to laws they are submitted to. Note that during the data transfer, even by using SSL/TLS protocols, the IP address are visible. Solutions to IP anonymity are commonly provided by \textit{trusted} VPNs, TOR\cite{Dingledine2004Tor:Router}, or darknet services like Freenet, I2P\cite{Delmer2009LemergenceI2p}, etc. Also, it can be noted that encryption keys could be stolen if vulnerabilities are found like heartbleed\cite{Mehta2014TheBug}. Indeed, advanced security for anonymity requires some specific software to run, and could be discouraging or even dangerous for uneducated people. Plus, the more protection via encryption is used, the more data is \textit{lost} for the human legacy. Indeed we cannot archive or index encrypted data.

The goal for this Bachelor Project is to try to answer the question: 

\textbf{Is it possible to provide a distributed data storage solution that prevents spying, and that simultaneously doesn't open a Pandora box for illegal and unethical data exchange?}

The foundations for this project have been done during the Spring Project\cite{Claret2016OvercloudsSpringSession}, which goal was to prepare the material and planning for the Bachelor Project. The work done during the cited project was mainly doing literature research and prototypes for browser only communication, encryption, and consensus.




%-------------------------------------------------------
%    END OF OBJECTIVES PAGE
%-------------------------------------------------------

