%-------------------------------------------------------
%    DOCUMENT CONFIGURATIONS
%-------------------------------------------------------

%-------------------------------------------------------
%    START OF CONCLUSION
%-------------------------------------------------------
\section{Conclusion}
Overclouds project is fascinating and challenging, there is much material to research and learn. It was said in the specification of this Spring Project that the wheel should not be reinvented, it is true, much work and progress has been made in this field for the past six years. As it is until now, for the communication and cryptography part, it is just a matter of fusing the knowledge to innovate in the field.

\paragraph{Planning}
Mistakes have been made during the initial planning. The student has bitten off more than he could chew, which led into rescheduling and reducing considerably the research that wanted to be done.

\paragraph{Architecture}
The architecture evolved three times, and it more than probable that it will evolve again. Currently, it looks more like a mind map, figure ~\ref{fig:latest-architecture}. However, we believe that the hot spots have been drafted and that Overclouds' big picture is respected.

\paragraph{Communication}
We proved that communications can be done from the browser with the need of dedicated third party servers. Provided results from the prototype are very promising.

\paragraph{Encryption}
Javascript is capable of providing client side data encryption required for the transactions and storage, which continues to confirm that a browser-only solution for Overclouds is conceivable.

\paragraph{Consensus}
This subject has not been treated yet, it is, however, in the Bachelor Project backlog. The general concept starts to get out of the fog. Indeed, looking at the block-chains technology, proof-of-participation, proof-of-activity, the Maidsafe-like concept of small groups of random nodes, and Ethereum fuel concept makes us believe that something could emerge our Consensus concept based on what we consider good ideas.

\paragraph{Bachelor Project}
Learning from is still the first result at school, for the BP, the planning will carefully reschedule during the first week, then controlled every week. Indeed, the student has a bad habit to be scattered because everything is interesting, and needs to be done at the moment. Man-hours should be watched as well.

%-------------------------------------------------------
%    END OF CONCLUSION
%-------------------------------------------------------