%-------------------------------------------------------
%    DOCUMENT CONFIGURATIONS
%-------------------------------------------------------

%-------------------------------------------------------
%    START OF CONCLUSION
%-------------------------------------------------------
\section{Conclusion}
Overclouds' project is fascinating and challenging, there is much material to research and learn. It was said in the specification that the wheel should not be reinvented, it is true, much work and progress has been made in this field for the past six years. As it is until now, it is just a matter of fusing the knowledge to innovate in the field.

\paragraph{Planning}
The required man hours have been respected. The project has met unplanned problems with Ethereum while working with the javascript implementation. However, the focus has been put on the storage and the results looks promising.

\paragraph{Architecture}
The architecture evolved from the spring session, and we believe that Overclouds' big picture is respected.

\paragraph{Encryption}
Javascript is capable of providing client side data encryption required for the transactions and storage.

\paragraph{Storage}
The bittorrent javascript implementation, webtorrent, has proven to work and responding to our current need.

\paragraph{Consensus} The ethereum javascript implementation didn't allow us to provide much work into the consensus itself, however it theoretically possible.

\paragraph{Webgate} We implemented a gateway accessible from the browser and allowing to share and load webapps.

%-------------------------------------------------------
%    END OF CONCLUSION
%-------------------------------------------------------
