%-------------------------------------------------------
%    START OF DESCRIPTION PAGE
%-------------------------------------------------------
\begin{titlepage}
{ \huge \bfseries Description}\\[0.2cm]

%-------------------------------------------------------
%    ENGLISH SECTION
%-------------------------------------------------------
{ \bfseries English}\\[0.2cm]

The initiative behind this project is to create a new generation of decentralized services to offer data sharing with a digital democracy over Internet. The services also want to be adapted to today's paranoia about Internet privacy as well as the preservation of knowledge for the next human generations.

The idea is to give the ability to the user to not rely on corporate servers, or farms of servers (cloud) anymore. With Overclouds, all users are now anonymous nodes connecting one to another freely and anonymously, with the goal to share and store data.

The network is a consensus of nodes. The data is moving from a node to another across the network via other nodes and ruled by the laws created by the community of users and accepted by consensus.

The project aims into the next generation of technologies to bring users a user-friendly interface without any kind of download and installation on their machine. To access the Overclouds service the only requirement it to use a standard browser and an Internet connection.

\clearpage
%-------------------------------------------------------
%    ENGLISH SECTION
%-------------------------------------------------------
{ \bfseries French}\\[0.2cm]

Le but de ce project est de créer des services décentralisés de nouvelle génération, afin de permettre un partage des données avec une démocratie numérique sur Internet. Ces services se veulent également adaptés à la paranoïa actuelle concernant la vie privée sur Internet ainsi qu'à la préservation des connaissances pour les prochaines générations de l'humanité.

L'idée est de donner à l'utilisateur la possibilité de ne plus compter sur des serveurs tiers, ou des fermes de serveurs (cloud) appartenant à des entreprises. Avec Overclouds, tous les utilisateurs sont des nœuds anonymes reliés les uns aux autres librement et anonymement, dans le but de partager et de stocker des données.

Le réseau est un consensus de noeuds. Les données sont en mouvement d'un noeud à un autre à travers le réseau via les autres nœuds et sont régies par les lois créées par la communauté des utilisateurs et acceptées par consensus.

Le projet vise les prochaines générations de technologies pour apporter aux utilisateurs une interface conviviale sans installation d'aucune sorte sur leur machine. Pour accéder aux services Overclouds, la seule condition est d'utiliser un navigateur standard et une connexion Internet.

\end{titlepage}

%-------------------------------------------------------
%    END OF DESCRIPTION PAGE
%-------------------------------------------------------