%-------------------------------------------------------
%    DOCUMENT CONFIGURATIONS
%-------------------------------------------------------

%-------------------------------------------------------
%    START OF RESULTS
%-------------------------------------------------------
\section{Results}

\subsection{Consensus} Research as theoretically proven that it's possible to use Ethereum has Overclouds' consensus. However, the implementation right from the browser has not been made, and the contracts are not implemented either.

\subsection{Webgate} We could use the WebTorrent\cite{Torrent2015WebTorrent} protocol in combination with our serverless concept to not relying on signaling servers to connect users together. The service is virtually accessible at any time as long as the user have an internet connection. The data can be shared encrypted and loaded as webapps. However, the decryption implementation has not been made.

\subsection{Iterations} Below the results for each weekly iterations (sprints)
\paragraph{Sprint 1} The consensus concept based on Ethereum smart contracts and planning for the next sprints.
\paragraph{Sprint 2} Testing and deploying ethereum with go, rust, and cpp clients. Finding a lot of issues with the Javascript implementation.
\paragraph{Sprint 3} Mesh of trust concept introduced the proof of participation, due to unsolvable problems with ethereum javascript client a replanning has been made, the focus for the next sprint is on the decentralized storage.
\paragraph{Sprint 4} Research on decentralized storage. The best option was to use webtorrent due to the bittorrent protocol and the existing browserified version. In parallel, we are still trying to fix your ethereum problems (DAO attack didn't help at all).
\paragraph{Sprint 5} Made and deployed a basic implementation for decentralized webapp using Webtorrent. 
\paragraph{Sprint 6} Data tribunal and data management research lead to the webgate concept. 
\paragraph{Sprint 7} Webgate implementation with quick share, SSL encryption, and a webapp demo for videos.
\paragraph{Sprint 8} Finalizing the Webgate and adding encryption for the data sharing.

\subsection{Webgate UI} Starting from the concept UI on the figure~\ref{fig:oc-concept-webgate-ui} from the annexes, we are now providing a modern UI for sharing and load content on Overclouds. The final version is of course still a prototype, however, accessible from \url{https://overclouds.ch}. Screenshots from the prototype UI are found on figures from the annexes.

%-------------------------------------------------------
%    END OF RESULTS
%-------------------------------------------------------
