%-------------------------------------------------------
%	DOCUMENT CONFIGURATIONS
%-------------------------------------------------------

%-------------------------------------------------------
%	START OF CRYPTOGRAPHY STATE OF THE ART
%-------------------------------------------------------
\subsubsection{Cryptography}
\paragraph{Stanford Javascript Crypto Library\cite{Stark2009SymmetricJavascript}}
\cite{University2009StanfordLibrary}
\blockquote{The Stanford Javascript Crypto Library (hosted here on GitHub) is a project by the Stanford Computer Security Lab to build a secure, powerful, fast, small, easy-to-use, cross-browser library for cryptography in Javascript.}

\paragraph{MSR JavaScript Cryptography Library}
Description from the official website \cite{Microsoft2015MSRLibrary}
\blockquote{The Microsoft Research JavaScript Cryptography Library has been developed for use with cloud services in an HTML5 compliant and forward-looking manner.}

\paragraph{MDN}
Description from the official website \cite{MDN2015MDNCrypto}
\blockquote{The Crypto interface represents basic cryptography features available in the current context. It allows access to a cryptographically strong random number generator and to cryptographic primitives.

An object with this interface is available on Web context via the Window.crypto property.}

\paragraph{W3C}
Description from the official website \cite{Sleevi2014WebAPI}
\blockquote{This specification describes a JavaScript API for performing basic cryptographic operations in web applications, such as hashing, signature generation and verification, and encryption and decryption. Additionally, it describes an API for applications to generate and/or manage the keying material necessary to perform these operations. Uses for this API range from user or service authentication, document or code signing, and the confidentiality and integrity of communications.}

\paragraph{Google Closure}
Description from the official website \cite{Google2015ClosureLibrary}
\blockquote{The Closure Library is a broad, well-tested, modular, and cross-browser JavaScript library. You can pull just what you need from a large set of reusable UI widgets and controls, and from lower-level utilities for DOM manipulation, server communication, animation, data structures, unit testing, rich-text editing, and more.}

\paragraph{forge}
Description from the official website \cite{DigitalBazaar2016Forge}
\blockquote{The Forge software is a fully native implementation of the TLS protocol in JavaScript as well as a set of tools for developing Web Apps that utilize many network resources.}

\paragraph{jsHashes}
Description from the official website \cite{Johnston2015JsHashes}
\blockquote{Fast and dependency-free cryptographic hashing library for node.js and browsers (supports MD5, SHA1, SHA256, SHA512, RIPEMD, HMAC)}

\paragraph{crypto-broserify}
Description from the official website \cite{Tarr2013Crypto-Browserify}
\blockquote{The goal of this module is to reimplement node's crypto module, in pure javascript so that it can run in the browser.}

\paragraph{BLAKE2\cite{SaarinenM-J.2015TheMAC}}
Description from the paper Analysis of BLAKE2 \cite{Guo2014AnalysisBLAKE2}
\blockquote{Recently proposed and already in use tweaked version of the SHA-3 finalist BLAKE.}

%-------------------------------------------------------
%	END OF CRYPTOGRAPHY STATE OF THE ART
%-------------------------------------------------------