%-------------------------------------------------------
%    DOCUMENT CONFIGURATIONS
%-------------------------------------------------------

%-------------------------------------------------------
%    START OF EXISTING NETWORKS STATE OF THE ART
%-------------------------------------------------------
\subsubsection{Existing Networks}
The most common form of networks approaching our project's vision are called \textit{Darknets}\cite{Biddle2003TheProtection} and they started to emerge during the years 2000ish\cite{Delmer2009LemergenceI2p}. They are all aiming to encrypt data transmissions and protect network's users from being spied on and bypass censorship.

\paragraph{Freenet\cite{Clarke1999ASystem,Clarke2001Freenet:System}}
Freenet is free software which lets you anonymously share files, browse and publish \textit{freesites} (web sites accessible only through Freenet) and chat on forums, without fear of censorship. Freenet is decentralised to make it less vulnerable to attack, and if used in \textit{}darknet mode, where users only connect to trusted nodes (real life friends, etc.), is very difficult to detect. 

Communications on Freenet nodes are encrypted and are routed through other nodes to make it extremely difficult to determine who is requesting the information and what its content is.

Each user contributes to the network by giving bandwidth and a portion of their hard drive for storing files. Files are encrypted, so generally the user cannot quickly discover what is in his \textit{datastore}. Chat forums, websites, and search functionality, are all built on top of this distributed data store.

\paragraph{I2P\cite{Foodists2003TheInternet}}
Originally IIP\cite{IIP2003InvisibleProject}. The Invisible Internet Project is an anonymous network, exposing a simple layer that applications can use to anonymously and securely send messages to each other. The network itself is strictly message based, but there is a library available to allow reliable streaming communication on top of it (a la TCP). All communication is end to end encrypted (in total there are four layers of encryption used when sending a message), and even the end points ("destinations") are cryptographic identifiers (essentially a pair of public keys).

\paragraph{MaidSafe\cite{MaidSafe2014MaidSafe.netCommunity}}
The SAFE (Secure Access For Everyone) Network is made up of the unused hard drive space, processing power and data connection of its users. It offers a level of security and privacy not currently available on the existing Internet and turns the tables on companies, putting users in control of their data, rather than trusting it to organizations.

\paragraph{Tor\cite{Dingledine2004Tor:Router}}
Tor is free software and an open network that helps you defend against traffic analysis, a form of network surveillance that threatens personal freedom and privacy, confidential business activities and relationships, and state security.

\paragraph{ZeroNet\cite{Zeronet2016ZeroNet}}
Real-time updated, P2P websites using Bitcoin cryptography and the BitTorrent network. Zeronet is decentralized, open source software in Python aimed to build an Internet-like computer network of peer-to-peer users. It is not anonymous by default, but users can hide their IP address by using Tor which uses Bitcoin cryptography and the BitTorrent network.

\paragraph{Project Maelstrom}
BitTorrent wants your help creating a P2P-powered web with Project Maelstrom. (Beta on Windows only)
The Maelstrom Network - currently under hectic development - is gearing up to be able to provide users and developers a joined interface to each other. Unlike some distinct offerings out there, this isn't a social network, and it never will be. All your information is for your eyes only until you allow an application to use it. We're trying to get web applications to a first class status on the web, similar to how an application on your computer is tightly integrated into the rest of the computer.

\paragraph{Diaspora*}
The community-run, distributed social network. diaspora* is based on three key philosophies: Decentralization, Freedom, and Privacy.

\paragraph{FlowingMail}
FlowingMail is the name of a new decentralized, secure and encrypted email protocol.
The most used email systems rely on a central server that receives, stores and forward the messages: FlowingMail is decentralized and does not rely on a central server to deliver the encrypted emails.
The scope of the FlowingMail protocol is to hide the information being transmitted and the parties involved in the communication.
The main component of the FlowingMail protocol is a Kademlia Distributed Hash Table (DHT), which is responsible for storing the encrypted emails while they are in transit and the certificates of the participants in the FlowingMail network.

\paragraph{Bitmessage\cite{Warren2012Bitmessage:System}}
Bitmessage is a P2P communications protocol used to send encrypted messages to another person or to many subscribers. It is decentralized and trustless, meaning that you need-not inherently trust any entities like root certificate authorities.

\paragraph{Retroshare}
RetroShare is free software for encrypted filesharing, serverless email, instant messaging, chatrooms, and BBS, based on a friend-to-friend network built on GPG. It is not strictly a darknet since optionally, peers may communicate certificates and IP addresses from and to their friends.

\paragraph{MediaGoblin\cite{Webber2016GNUDocumentation}}
MediaGoblin is a free software media publishing platform that anyone can run. You can think of it as a decentralized alternative to Flickr, YouTube, SoundCloud, etc.

\paragraph{Movim}
My Open Virtual Identity Manager is a distributed social network built on top of XMPP, a popular open standards communication protocol. Movim is a free and open source software licensed under the AGPL. It can be accessed using existing XMPP clients and Jabber accounts.

\paragraph{The IPFS Project\cite{Benet2014IPFS-ContentSystem}}
The InterPlanetary File System is a new hypermedia distribution protocol, addressed by content and identities. IPFS enables the creation of completely distributed applications. It aims to make the web faster, safer, and more open. IPFS claims to be a Permanent Web with a new peer-to-peer hypermedia protocol.

\paragraph{Serval Project\cite{Gardner-stephen2011TheTelecommunications}}
Serval is a telecommunications system comprised of at least two mobile phones that are able to work outside of regular mobile phone tower range due thanks to the Serval App and Serval Mesh.

\paragraph{Open Garden}
Open Garden's technology creates a software-based network, also known as a peer-to-peer wireless mesh network, among participating mobile devices using WiFi, Bluetooth LE, and other technologies. Open Garden's innovations include: seamless device discovery and pairing, offline identity, a proprietary network protocol for addressing and routing messages off-the-grid, distributed algorithms for managing mesh networks, advanced traffic management (multi-hop, store and forward), and battery use reduction.

\paragraph{Hyperboria\cite{HypeHyperboriaWhitepaper}}
A community of local Wifi initiatives, programmers, and enthusiasts. They are running a peer-to-peer IPv6 network with automatic end-to-end encryption, distributed IP address allocation, and DHT-based Source Routing.

%-------------------------------------------------------
%    END OF EXISTING NETWORKS STATE OF THE ART
%-------------------------------------------------------