%-------------------------------------------------------
%	DOCUMENT CONFIGURATIONS
%-------------------------------------------------------

%-------------------------------------------------------
%	START OF TECHNOLOGIES STATE OF THE ART
%-------------------------------------------------------
\subsubsection{Technologies}
\paragraph{QEMU JS}
\cite{Bellard2015JavascriptEmulator}
\blockquote{It is a generic and open source machine emulator and virtualizer.}

\paragraph{PeerJS}
Description from the official website \cite{SwitchPeerJS}
\blockquote{PeerJS is a service which makes it easier to build a chat room using the present WebRTC's PeerConnection API. The PeerConnection API proposes to be able to send data, video etc from one user-agent to another without the need for it going through a server. PeerJS handles this handshake with a simple Socket.IO backend server.}

\paragraph{PeerShare}
Description from the official website \cite{CuonicPeerShare}
\blockquote{PeerShare is a P2P file sharing website that uses WebRTC technologies to allow uses to send and receive files without going through any servers. PeerShare is mainly built on Javascript and jQuery and uses PeerJS as a WebRTC API.}

\paragraph{PeerSurf}
Description from the official website \cite{HaywardPeerSurf}
\blockquote{PeerSurf is a demo (and kind of a library) of P2P websites powered by WebTorrent}

\paragraph{OpenWebRTC}
Description from the official website \cite{OpenWebRTCOpenWebRTC}
\blockquote{With OpenWebRTC you can build native WebRTC apps that communicate with browsers that supports the WebRTC standard, such as Chrome, Firefox and Bowser. OpenWebRTC is especially focused on mobile platforms, with powerful features such as hardware accelerated video coding and OpenGL-based video rendering.}

\paragraph{PeerServer}
Description from the official website \cite{Server2013PeerServer}
\blockquote{This system allows you to quickly create a decentralized, short-lived web application where all the content lives within your browser. The traditional server only performs the initial handshake between the client-browsers and the client-server; your browser serves all other content peer-to-peer.}

%-------------------------------------------------------
%	END OF TECHNOLOGIES STATE OF THE ART
%-------------------------------------------------------