%-------------------------------------------------------
%	DOCUMENT CONFIGURATIONS
%-------------------------------------------------------

%-------------------------------------------------------
%	START OF TRANSFER PROTOCOLS STATE OF THE ART
%-------------------------------------------------------
\subsubsection{Transfer Protocols}

\paragraph{Route-based VPN}
\cite{Point2014VPNR76}
\blockquote{The use of VPN Tunnel Interfaces (VTI) introduces a new method of configuring VPNs called Route Based VPN. This method is based on the notion that setting up a VTI between peer Security Gateways is much like connecting them directly.}

\paragraph{Commotion}
Description from the official website \cite{CommotionCommunityNetworks}
\blockquote{Commotion is an open-source communication tool that uses wireless devices to create decentralized mesh networks.}

\paragraph{Hubzilla}
Description from the official website \cite{HubzillaHubzilla}
\blockquote{Hubzilla is a powerful platform for creating interconnected websites featuring a decentralized identity, communications, and permissions framework built using common webserver technology.}

\paragraph{Tent}
Description from the official website \cite{Tent.is2013Tent.io}
\blockquote{Tent lets you control your data instead of handing it over to service and app providers. Just like email, you choose a provider or can set up your own Tent server. Tent data and relationships are portable so you can change Tent providers easily at any time.}

\paragraph{cjdns}
Description from the official website \cite{CjdnsCjdns}
\blockquote{Networking Reinvented. Cjdns implements an encrypted IPv6 network using public-key cryptography for address allocation and a distributed hash table for routing. This provides near-zero-configuration networking and prevents many of the security and scalability issues that plague existing networks.}

\paragraph{WebRTC}
Description from the official website \cite{GoogleWebRTC}
\blockquote{WebRTC is a free, open project that provides browsers and mobile applications with Real-Time Communications (RTC) capabilities via simple APIs. The WebRTC components have been optimized to best serve this purpose.} http://iswebrtcreadyyet.com

\paragraph{Open Peer}
Description from the official website \cite{Hookflash2014OpenPeer}
\blockquote{
Real-time Communications Protocol \& Specification. What further reduces the proliferation of peer-to-peer is a lack of standardization, openness and ubiquity of the technology. The standards bodies have been working for years on firewall traversal techniques and standardization of the approaches and a new joint effort called WebRTC between the W3C and IETF on how browsers can directly communication between browsers to move media. This joint effort does not specify how signalling happens between peers so it’s not a complete solutions on its own.}

\paragraph{freedom.js}
Description from the official website \cite{Freedom.js2012Freedom.js}
\blockquote{It's a framework for building peer-to-peer (P2P) web apps. Easily create social applications that work in modern web browsers, Chrome packaged apps, Firefox extensions, node.js, and native mobile apps. freedom.js apps are just JavaScript, so they can be distributed as packages on an app store or hosted on static web servers.}


%-------------------------------------------------------
%	END OF TRANSFER PROTOCOLS APPS STATE OF THE ART
%-------------------------------------------------------