%-------------------------------------------------------
%    DOCUMENT CONFIGURATIONS
%-------------------------------------------------------

%-------------------------------------------------------
%    START OF BIG PICTURE PAGE
%-------------------------------------------------------
\subsection{The Big Picture}
After being introduced to the project, let us present our current vision for the outcome of Overclouds. Note that the result is not the bachelor project, allocated man-hours are clearly not enough. Of course, due to the early stage of the project, the vision may evolve. The bachelor work will aim to produce parts of the vision.

\paragraph{Global}
We are aiming at providing a product easy to use, technophobe-friendly, that does not require any external software. We are focusing on the browser experience; any browser should be able to run the network. The user would be able to use any hardware and main net connections to join the network, very low bandwidth, very low computational power, Hyperboria\cite{HypeHyperboriaWhitepaper} compatible, or even nonexistent technologies yet. The security allows to for any user to be ISP anonymous and censorship-resistant. Plus, any user could access its personal \textit{desktop} with data right from any browser on the main net.

\paragraph{The consensus}
A consensus-driven network with unlimited power over the entire network. Putting the digital democracy to the top. It works in harmony with the newly introduced concept of \textit{Mesh-of-Trust} which glues identities and nodes and certifying nodes' hardware and identities. The mesh-of-trust plays the role of data manager and data tribunal.

\paragraph{Network}
A serverless mesh of self-aware and smart nodes. Every transaction is verified and is mathematically elegant. Intelligent enough for self-preservation, and bypass consensus decisions if they judged as self-destruction. Privacy is being an integrant part of any layer of the network. However, a consensus decision can always bypass any rule. A registry name could be available to access easily the network from browser's URL (.over?).

\paragraph{Storage}
The network is using cooperative nodes to store and process computational work. Data has many stats, private, public, time to live, or countdown to go public. Meaning that anonymous websites can be hosted.

\paragraph{Crypto-Currency}
Consensus-driven currency, the genesis block is modifiable. Nodes are automatically contributing to the network wealth. Units of the currency are rewarded by the consensus to identities as a reputation value. The currency represents how an identity \textit{respect} on the network, which could give him leadership powers like a stronger vote power in specific cases determined by the consensus.

\paragraph{Self updating}
An ultimate achievement would be a self-programmed network driven by the consensus.\cite{Gabel2008DynamicallyDevelopers}

%-------------------------------------------------------
%    END OF BIG PICTURE PAGE
%-------------------------------------------------------