%-------------------------------------------------------
%    DOCUMENT CONFIGURATIONS
%-------------------------------------------------------

%-------------------------------------------------------
%    START OF INTRODUCTION PAGE
%-------------------------------------------------------
\subsection{Introduction}
\paragraph{Today} The world and more particularly the digital world has an important concern for privacy. Indeed, Edward Snowden's revelations on NSA's massive spying\cite{EdwardSnowdenArchive} led to a massive media scandal. People started to feel that their digital privacy was at stake by the worldwide "spies", either the government, companies, or even unknown treats yet. Resulting that the internet community evolved and it became an important economical and political part.

\paragraph{New behaviors emerged} Right into the web users, a noticeable split has been made, into two classes of people. Individuals who don't know how to protect their privacy on the Internet, and people who do know how to protect their privacy. For the first group, some are not aware of the global privacy status, some don't care and some don't know how to protect themselves. Concerning the second panel, we have some personal ethical problems, which led to this project.

\paragraph{The problem} It's understood that people want to avoid advertising companies' and governments' tracking. It's also known that some people are scared that their stole private data could be exposed publicly. However, some private data must be sometimes public and some cases forced to be made public. From our humanistic and unpolitical point of view, we believe, that the data from terrorist groups (including their members and partisan) have to be denounced, made public and the locking the data into a secured safely. Why archiving and not just deleting them? We, again, believe that regardless how bad the data is (as seen today), it's still part of our history, and it's our duty to preserve them as a legacy for future generation to understand and learn from what we are mistakes today.

\paragraph{Intellectual Properties} Read as IP. Our social and political evolution led to copyright laws, which prohibit the free sharing of any kind of data such as art and knowledge by default. Indeed, our culture specifies that any intellectual discovery or advancement is by default protected by copyrights (we will not discuss the process here neither the manipulation of the copyright system). This led usually into knowledge or data retention, which makes us feel that the IP system is serious treat for our humanity legacy.

\paragraph{Economy} However, it's also understood that with our economical system, people need to make a living out of the IP, which leads into higher protection for their data. Our digital method of protection is to encrypt the data with a digital key provided by the owner (generally companies). The encrypted data is then stored in data centers or on hard-drives (which could some times be bad for the long term preservation). Owners then have the choice of sharing their (copyrighted) material and are usually also choosing to use encrypted manners to distribute them. The transmission protection is to unable people from looking at them without owners' consent (usually money) and redistributing them with consent (not making money out of it). So,  the data is protected for the storage, during transmission, and we also have DRMs technology that only descrypts the piece of data you are looking at on the fly. So, technically, the full data is never in clear anymore.

\paragraph{Game of cat and mouse} Some people are protecting data, other are trying to break the protection to retrieve them. And they both use encryption technologies to secure their transmissions. Meaning that the owners are protecting their data, and the \textit{thief} are also protection the stolen data to not by caught. At the end the same data is being transmitted anyway but never in clear. This procedure make us believe that something is wrong with the system and that it could be considered as a treat for the humanity global knowledge and culture.

\paragraph{Legacy} We are confronted with another ethical problem. We are entering into a fully encrypted data era, which will make all our data appear as a bunch of random noises that for various reasons are bad for us. We would like you to think about how all our global knowledge is and will be sorted in the near future. Data such as art or knowledge, how will our next generations of humans be able to retrieve it in a few years? How can we be sure that the unbreakable keys (quantum proof, etc.) that we are making today will not be lost?
Now think about the idea of randomizing (with encryption noises) our communication signals that we are sending into outer space? The signals that we are sending out to space are already today much different from what it looked like in the sixties. For example, purely analog signals (TV, FM radios) are depreciated and got replaced with numerical transmission (DVB, DAB), and of course most of them are encrypted (pay-to-watch tv, pay-to-listen radios). Moreover, our communication technologies involve into higher frequencies and always fewer power consumption. All this is resulting into the fact that today, Earth radiates probably much fewer waves than before and seen as random noises.

\paragraph{Taking the wrong direction} It's easily imaginable that soon a company will say: "Hey, we are specialized in transmitting encrypted data, nobody will ever know what you are doing, and when you are doing it. All you have to do is to buy from us, with a crypto-currency, a key every month.". See this has an evolution of the VPN services. We don't have a sharp opinion on neither it's a good or a bad thing. However, it will create a privatization of the data security, and it most likely to destroy any hopes of retrieving the encrypted data one day.

\paragraph{Overclouds} The project aims into a new approach for protecting people's privacy and ensure a legacy for future generations.
The main idea is that Overclouds is a consensus-driven anonymous network of nodes with storage and computation power. Each node is aware of other nodes, but they are unable by default to identify this owner on the main net (whatever the physical technology of communication at any given point of time). The consensus, as limitless power over the network. It can, for example, decide to disclose the physical location of particular nodes, if they considered malicious or bad for the rest of the network (such as terrorists, scammers, black hats, etc.).

\paragraph{Nice to have} We also would like that Overclouds was designed to not act like random noises. Preferably, external and internal listener or watcher should see a nice mathematically driven signal. The mathemagical behind it would allow any source node to predict exactly how its data is will handled by default by the consensus. However, it should be unpredictable for other nodes, but still elegant to look at.

%-------------------------------------------------------
%    END OF INTRODUCTION PAGE
%-------------------------------------------------------
