%-------------------------------------------------------
%    DOCUMENT CONFIGURATIONS
%-------------------------------------------------------

%-------------------------------------------------------
%    START OF MANAGEMENT PAGE
%-------------------------------------------------------
\subsection{Management}
An iterative approach has been used during the progress of the project. So, the SCRUM methodology was chosen. The Backlog and the Sprint advances can be found in the annexes.

Originally six sprints were planned. However, the status of the project was going as fast as intended. Finally, we ended up with four sprints and two replannings.

Indeed, an error was made by the student during the initial planning; he planned the scrums based on results and not man-hours (86h) which were in fact about 8.6h per week during ten weeks. However, the required work per week to produce the scrum results was largely above. We noticed at week three that something was not right, resulting into forcing to control that the 8.6 hours were not exceeded. We noticed that 43 hours were made instead of 34.4, and decide on week 5 to do a new planning with one week increase on the current sprint.

The planning was remade for the second time in week 6, 46 hours was produced at that point in time for 43 required. The number of scrum schedule got reduced into four sprints, and by this means moving two research themes into the bachelor backlog.

At the end of the 10th week, the student spent 131h for 81h required hours.

It is important to point out that the problems did not only come from the unrealistic first planning, expect if the research was done very lightly, but the prototype would not have been something to rely on. The student was a bit too much interested about the new world is was discovering and started to do maybe to deep research into each treated subjects, times flew much faster than expected, and time was missing in the end for the planning.

The last two weeks got very expensive in time with the goal to deliver the report with the research done, even planned research.

For the Bachelor planning, the man-hours will be more carefully looked at, and adjust the planning right away if something is not going has planned.

%-------------------------------------------------------
%    END OF MANAGEMENT PAGE
%-------------------------------------------------------