%-------------------------------------------------------
%    DOCUMENT CONFIGURATIONS
%-------------------------------------------------------

%-------------------------------------------------------
%    START OF OBJECTIVES PAGE
%-------------------------------------------------------
\subsection{Objectives}
The goal in for this Spring Project is to prepare the material and planning for the Bachelor Project. The work done during this project is mainly doing literature research and prototyping by iteration. Indeed, we are looking to help the start of the bachelor project with various defined aspects, concepts, and prototypes.

Can we provide a distributed data storage solution that prevents espionage and that simultaneously doesn't open a pandora box of illegal and ethical data exchange? It's the question we will be trying to answer during the bachelor project.

As it is today, the data is centralized into specific operators like Google, Facebook, Dropbox, Tor hidden services, and much more (expect of services like Freenet\cite{Clarke2001Freenet:System}). They are usually using encrypted protocol to transmit data to their client, but are most of the time stored in clear on their cloud servers. Sometimes the data is stored encrypted, but the operators must comply with the local laws of the data centers, which could compromise the security. The user could encrypt the data himself, however technical knowledge is required and sometimes the rules of the storage operators doesn't allow homemade security due to laws they are submitted to. Note that during the data transfer, even by using SSL or TLS protocols, the IP address are visible. Solutions to IP anonymity are commonly provided by (trusted) VPNs, TOR\cite{Dingledine2004Tor:Router}, or darknet\cite{Delmer2009LemergenceI2p} services like Freenet, I2P\cite{Delmer2009LemergenceI2p}, etc. Plus encryption keys could be stolen if vulnerabilities are found like heartbleed\cite{Mehta2014TheBug}. Indeed, advance security for anonymity requires some specific software to run, and could be discouraging or even dangerous for uneducated people. Plus, the more protection via encryption is used, more data is \textit{lost} for the human legacy, we cannot archive or index encrypted data.

%-------------------------------------------------------
%    END OF OBJECTIVES PAGE
%-------------------------------------------------------