%-------------------------------------------------------
%    DOCUMENT CONFIGURATIONS
%-------------------------------------------------------

%-------------------------------------------------------
%    START OF CONSENSUS ANALYSE
%-------------------------------------------------------
\subsection{Consensus}
Read this subsection as a teaser from the final project analysis on the consensus concept. Indeed, the time allocated for this research and analyze was null, however knowledge grows over time even if the research was trageting something else.

\subsubsection{Consensus != Block-chains}
The block-chains technology being very popular nowadays, it sometimes can put eye cups on our field of decisions.

Block-chains have indeed proved that it works as a consensus. However, a consensus with highly fault tolerant networks and overcome the Byzantine (Two Generals Problem) is not something that only block-chains have.

Just for taking one example, Maidsafe\cite{MaidSafe2014MaidSafe.netCommunity} uses another technology to obtain a consensus\cite{Nick2015CONSENSUSBLOCKCHAIN}. Instead of using the whole network to validate a transaction, they give the consensus role to a random group of nodes.

\paragraph{Comparing} They both have pros and cons of course.
\begin{itemize}
\item Block-chains
\begin{itemize}
\item Pros: Shared global record of all transactions.
\item Cons: The chain can be gigantic (Bitcoin more than 60GB at the moment), and the file must be synced between all network’s 6000 plus. Network speed. nodes\cite{AyeowchGLOBALDISTRIBUTION}.
\end{itemize}
\end{itemize}
\begin{itemize}
\item MaidSafe
\begin{itemize}
\item Pros: Bandwidth speed limitations only. Low data storage consumption.
\item Cons: Small groups of nodes are playing the role of consensus for transactions. Nodes could never be aware of transactions that happened elsewhere if they are not related to them at any point of time.
\end{itemize}
\end{itemize}

%-------------------------------------------------------
%    END OF BLOCKCHAINS ANALYSE
%-------------------------------------------------------